Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Move period after citation.

An election involves an information exchange between many independent \term{voters} and a single
\term{election authority}.
In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
by the election authority.
A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
reported by the election authority. \cite{preta}
Voting is complicated by the requirement that all votes remain secret to avoid coercion.

>>>>

An election involves an information exchange between many independent \term{voters} and a single
\term{election authority}.
In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
by the election authority.
A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
reported by the election authority \cite{preta}.
Voting is complicated by the requirement that all votes remain secret to avoid coercion.
